Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-03-25 paper.tex
Rearrange introduction and add to abstract

% Abstract (Less than 200 words)
\abstract{The acceptable Reynolds number mismatch for scaled physical model
testing a cross-flow turbine is investigated experimentally.}

@@

\subsection{Previous Work}
\todo[inline]{Add lit review here}

\subsection{Causes for Reynolds Number Dependence}

@@

>>>>

% Abstract (Less than 200 words)
\abstract{The acceptable Reynolds number mismatch for scaled physical model
testing a cross-flow turbine is investigated experimentally, both with respect
to prediction of full-scale performance, and wake characteristics, which will be
drivers of overall performance and interaction between multiple turbines.}

@@

\subsection{Reynolds Number Effects}
\todo[inline]{Add lit review here}

In this study we are focused on a turbine constructed from foils---a lift-driven
device in contrast to drag-driven. A logical starting point for understanding
the effects of $Re$ on overall turbine loading is to look at simplified cases
of individual foils, with respect to their static and dynamic loading.

\subsubsection{On Static Foil Behavior}

@@

\subsubsection{On Dynamic Foil Behavior}

Dynamic effects on blade loading can be distinguished between attached and
separated conditions.

\subsubsection{On Wake Flows}

\todo[inline]{What do studies in the literature tell us about $Re$ effects
on shear flows, wakes, and vortex flows?}
